GSE158422: DNA methylation in Lung squamous cell carcinoma - gene methylation enrichment analysis

### 2023-09-29 figs/GSE158422_split.Rmd
split and analyse

chragg <- function(mval,myann,cores=1){
  keep <- rownames(subset(myann,UCSC_RefGene_Name!=""))
  mx <- mval[rownames(mval) %in% keep,]
  chrs <- unique(anno$chr)
  myorder <- unlist(lapply(chrs,function(mychr) { nrow(subset(annodf,chr==mychr)) } ))
  chrs <- chrs[order(-myorder)]
  leadercores <- floor(sqrt(cores))
  workercores <- ceiling(sqrt(cores))
  chrmedf <- mclapply(chrs,function(chr) {
    annodf <- as.data.frame(anno)
    chrfrag <- annodf[annodf$chr==chr,]
    chrprobes <-rownames(chrfrag)
    chrmx <- mx[rownames(mx) %in% chrprobes,]
    chranno <- myann[rownames(myann) %in% chrprobes,]
    chrmedf <- magg(mval=chrmx,myann=chranno,cores=workercores)
    return(chrmedf)
  },mc.cores=leadercores)
  medf <- do.call(rbind, chrmedf)
  return(medf)
}

@@

splitanalyze_la <- function(seed){
  set.seed(seed)
  a <- sample(1:37,18)
  a <- a[order(a)]
  nona <- setdiff(1:37,a)
  set.seed(seed)
  b <- sample(nonctl,18)
  b <- b[order(b)]
  a <- c( (a*2)-1 ,a*2 )
  a <- a[order(a)]
  b <- c( (b*2)-1 ,b*2 )
  b <- b[order(b)]

@@

```{alfunc}

splitanalyze_al <- function(seed){
  set.seed(seed)
  a <- sample(1:37,18)
  a <- a[order(a)]
  nona <- setdiff(1:37,a)
  set.seed(seed)
  b <- sample(nonctl,18)
  b <- b[order(b)]
  a <- c( (a*2)-1 ,a*2 )
  a <- a[order(a)]
  b <- c( (b*2)-1 ,b*2 )
  b <- b[order(b)]

>>>>

chragg <- function(mval,myann,cores=1){
  annodf <- as.data.frame(anno)
  keep <- rownames(subset(myann,UCSC_RefGene_Name!=""))
  mx <- mval[rownames(mval) %in% keep,]
  chrs <- unique(anno$chr)
  myorder <- unlist(lapply(chrs,function(mychr) { nrow( annodf[annodf$chr==mychr,] ) } ))
  chrs <- chrs[order(-myorder)]
  leadercores <- floor(sqrt(cores))
  workercores <- ceiling(sqrt(cores))
  chrmedf <- mclapply(chrs,function(chr) {
    chrfrag <- annodf[annodf$chr==chr,]
    chrprobes <-rownames(chrfrag)
    chrmx <- mx[rownames(mx) %in% chrprobes,]
    chranno <- myann[rownames(myann) %in% chrprobes,]
    chrmedf <- magg(mval=chrmx,myann=chranno,cores=workercores)
    return(chrmedf)
  },mc.cores=leadercores)
  medf <- do.call(rbind, chrmedf)
  return(medf)
}

@@

```{r,laflow}

splitanalyze_la <- function(seed){
  set.seed(seed)
  a <- sample(1:37,18)
  a <- a[order(a)]
  nona <- setdiff(1:37,a)
  set.seed(seed)
  b <- sample(nona,18)
  b <- b[order(b)]
  a <- c( (a*2)-1 ,a*2 )
  a <- a[order(a)]
  b <- c( (b*2)-1 ,b*2 )
  b <- b[order(b)]

@@

```{r,alflow}

splitanalyze_al <- function(seed){
  set.seed(seed)
  a <- sample(1:37,18)
  a <- a[order(a)]
  nona <- setdiff(1:37,a)
  set.seed(seed)
  b <- sample(nona,18)
  b <- b[order(b)]
  a <- c( (a*2)-1 ,a*2 )
  a <- a[order(a)]
  b <- c( (b*2)-1 ,b*2 )
  b <- b[order(b)]
